
\chapter{References} % Main appendix title

$\\ $

Robert, A. (2010). A course in p-adic analysis. Springer. 

$\\ $

Afshari, B., \& Wehr, D. (2024). Abstract cyclic proofs. Mathematical Structures in Computer Science, 1–26. https://doi.org/10.1017/s0960129524000070 

$\\ $

Matiyasevich, Yuri. Word Equations, Fibonacci Numbers, and Hilbert's Tenth Problem.

$\\ $

Arnold, Andre \& Latteux, Michel. (1978). A New Proof of Two Theorems About Rational Transductions. Theoretical Computer Science 8.

$\\ $

Garg, Ankit \& Gurvits, Leonid \& Oliveira, Rafael \& Wigderson, Avi. (2016). A deterministic polynomial time algorithm for non-commutative rational identity testing. Annual Symposium on Foundations of Computer Science.

$\\ $

Weisstein, Eric W. "Field Axioms." From MathWorld--A Wolfram Web Resource. https://mathworld.wolfram.com/FieldAxioms.html

$\\ $

LeetCode - the world’s leading online programming learning platform. (n.d.). https://leetcode.com/ 

$\\ $

Valiant, Leslie., Holographic Algorithms.

$\\ $

Berstel, J., \& Reutenauer, C. (2010). Noncommutative rational series with applications. Cambridge University Press.

$\\ $

Sipser, M. (2006). Theory of Computation (2nd ed., p. 431). Course Technology, Cengage Learning.

$\\ $

Munkres, J. R. (2000). Topology (2nd ed., p. 537). Prentice Hall.

$\\ $

Artin, M. (2011). Algebra (2nd ed., p. 543). Pearson.

$\\ $

Enderton, H. B. (2001). Logic (2nd ed., p. 317). HARCOURT/ACADEMIC PRESS.

$\\ $

Lay, S. R. (2004). Analysis (4th ed., p. 394). Pearson Prentice Hall.

$\\ $

Cox, D. A., Little, J., \& O’Shea, D. (1997). Ideals, varieties, and algorithms: An introduction to computational algebraic geometry and commutative algebra (2nd ed.). Springer.

$\\ $

Golub, G. H., \& Van Loan, C. F. (1996). Matrix Computations (3rd ed., p. 728). Johns Hopkins University Press.

$\\ $

Hofstadter, D. R. (1999). Gödel, Escher, Bach: An eternal golden braid. Basic Books.

$\\ $

Cormen, T. H., Leiserson, C. E., Rivest, R. L., \& Stein, C. (2009). Introduction to Algorithms (3rd ed.). MIT Press.

$\\ $

Shilov, G. E. (2012). Linear algebra (R. A. Silverman, Trans.). Dover Publications. (Original work published 1971)

$\\ $

Strang, G. (2009). Introduction to Linear Algebra (4th ed., p. 585). Wellesley-Cambridge Press.

$\\ $

Rosen, K. H. (2006). Discrete Mathematics And Its Applications (6th ed.). McGraw-Hill Education.

$\\ $

Prasolov, V. V. (1995). Intuitive topology. American Mathematical Society.

$\\ $

Carter, N. (2009). Visual group theory. Mathematical Association of America.

$\\ $

Spivak, M. (2008). Calculus (4th ed., p. 680). Publish or Perish.

$\\ $

Sullivan, M. (2008). Precalculus (8th ed., p. 1152). Prentice Hall.

$\\ $

Ung, E. (2023). A Language of Polynomials (Version 1.0.0). 

$\\ $

Hamming, R. W. (1986). Numerical methods for scientists and engineers. Courier Corporation.

$\\ $

Weisstein, Eric W. "Field Axioms." From MathWorld--A Wolfram Web Resource. 

$\\ $

Pinter, C. C. (2010). A book of abstract algebra (2nd ed.). Dover Publications.

$\\ $

Ung, E. (2023). Applications For Monomial Deciders (Version 1.0.1).

$\\ $

Ung, E. (2023). A Language Of Polynomials (Version 1.0.1).

$\\ $

Ung, E. (2018). Inferring Lindenmayer Systems (Version 2.0.1).


