% Chapter Template

\chapter{Applications For Monomial Deciders} % Main chapter title

\label{ChapterX} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}


%----------------------------------------------------------------------------------------
%	SECTION 2
%----------------------------------------------------------------------------------------

\section{Starting With A Theorem Of Infiniteness}

This section assumes that both P=NP and P!=NP and the following sections will provide reasoning and examples.

\section{Mapping Out Representations}

This section contains my opinions of what mathematics is.

\section{Euler's Constant}

Euler's constant is an example of P = NP because of it's use of calculus.

$\\ $

To show that it is also in the problem set of P $\neq$ NP, start by using the picking function going into infinity.

$\\ $

$e = pf(x) = \theta(language\ of\ pf(x))$

$\\ $

$\left\{ x = x^2/x = x^3/x^2 = x^4/x^3 = x^5/x^4 = \cdots = x^n/x^{n-1} \right\}$

$\\ $

$1 + 1 + 1/(1+1) + 1/(3+3) + 1/(4+(4*3+4*2)+4)$

\section{Sketching Into Code}

There is a technique to develop code from a diagram of a decider. Take into account the degree of the states and that should account for the halting required to break from the loop.

\begin{lstlisting}
bool generalizedMD(int y)
{
    if (y == 0)
    {
        return true;
    }
    var s = y;
    while (s >= 0)
    {
        for (int i = 0; i < 2; i++)
        {
            for (int j = 0; j < 4; j++)
            {
                if (s == 0 && (j == 0 || j == 2) && i == 0)
                {
                    return true;
                }
                else if (s < 0)
                {
                    return false;
                }
                s -= 1;
            }
        }
    }
    return true;
}
\end{lstlisting}

\section{Gather Some Data}

Using the generalizedMD function where we make some sketch of the initial algorithm, we can collect some data Generate: 

f(x) = y on the first line

Negatives on the second

$\\ $

We notice that we need two finishing states and that all the ven y's end in one state and all the odd y's end on the other.

E: Is it even?

$\\ $

We create a for loop of $n^3$ that with constant 2 and count how many times it passes through the finishing state.

T: Total amount of times it passes the finishing state.

$\\ $

Insight is gained by noticing that the difference only increases every other time and that it increases by a difference of 2 every it passes a finishing state.

D: Difference of the number of hits to the finishing state between the alst time it is called and the first.

$\\ $

\begin{lstlisting}
// Generates negatives from a general monomial decider represented as an algorithm so
// that we can collect data about the negatives
int[] Generator(int max)
{
    int[] result = new int[max + 1];
    int x = 0;
    int negatives = 0;
    int i = 0;
    while (x < max + 1)
    {
        int num = 2 * (Convert.ToInt32(Math.Pow(x, 2)));
        if (generalizedMD(i))
        {
            // A simple verifier
            if (num == i)
            {
                Console.WriteLine(negatives);
                Console.WriteLine("f(" + x + ") = " + i);
                result[x] = i;

                x++;
                negatives = 0;
            }
            else
            {
                negatives++;
            }
        }
        i++;
    }

    return result;
}
\end{lstlisting}

\section{Representing Monomial Deciders As Code}

\begin{lstlisting}
// After getting some log results, we can construct a decider
bool MonomialDecider2xx(int y)
{
    var total = 0;
    var hits = 0;
    var diff = 1;
    var isEven = 0;
    var s = 0;

    while (s <= y)
    {
        for (int i = 0; i < 2; i++)
        {
            for (int j = 0; j < 2; j++)
            {
                for (int k = 0; k < 2; k++)
                {
                    if ((i == 0)&&(j == 0 || j == 1)&&(k == 0))
                    {
                        if (hits == total)
                        {
                            if (s == y)
                            {
                                Console.WriteLine(s + ": Hits: " + total);
                                return true;
                            }
                            else if (s > y)
                            {
                                return false;
                            }

                            total += diff;
                            isEven++;
                            if (isEven % 3 == 2)
                            {
                                isEven = 0;
                                diff += 2;
                            }
                        }

                        hits++;
                    }
                    s++;
                }
            }
        }
    }

    return false;
}
\end{lstlisting}

\section{Negative Numbers}

Sed ullamcorper quam eu nisl interdum at interdum enim egestas. Aliquam placerat justo sed lectus lobortis ut porta nisl porttitor. Vestibulum mi dolor, lacinia molestie gravida at, tempus vitae ligula. Donec eget quam sapien, in viverra eros. Donec pellentesque justo a massa fringilla non vestibulum metus vestibulum. Vestibulum in orci quis felis tempor lacinia. Vivamus ornare ultrices facilisis. Ut hendrerit volutpat vulputate. Morbi condimentum venenatis augue, id porta ipsum vulputate in. Curabitur luctus tempus justo. Vestibulum risus lectus, adipiscing nec condimentum quis, condimentum nec nisl. Aliquam dictum sagittis velit sed iaculis. Morbi tristique augue sit amet nulla pulvinar id facilisis ligula mollis. Nam elit libero, tincidunt ut aliquam at, molestie in quam. Aenean rhoncus vehicula hendrerit.

\section{Pi}

Sed ullamcorper quam eu nisl interdum at interdum enim egestas. Aliquam placerat justo sed lectus lobortis ut porta nisl porttitor. Vestibulum mi dolor, lacinia molestie gravida at, tempus vitae ligula. Donec eget quam sapien, in viverra eros. Donec pellentesque justo a massa fringilla non vestibulum metus vestibulum. Vestibulum in orci quis felis tempor lacinia. Vivamus ornare ultrices facilisis. Ut hendrerit volutpat vulputate. Morbi condimentum venenatis augue, id porta ipsum vulputate in. Curabitur luctus tempus justo. Vestibulum risus lectus, adipiscing nec condimentum quis, condimentum nec nisl. Aliquam dictum sagittis velit sed iaculis. Morbi tristique augue sit amet nulla pulvinar id facilisis ligula mollis. Nam elit libero, tincidunt ut aliquam at, molestie in quam. Aenean rhoncus vehicula hendrerit.


\section{Fibonacci}

Sed ullamcorper quam eu nisl interdum at interdum enim egestas. Aliquam placerat justo sed lectus lobortis ut porta nisl porttitor. Vestibulum mi dolor, lacinia molestie gravida at, tempus vitae ligula. Donec eget quam sapien, in viverra eros. Donec pellentesque justo a massa fringilla non vestibulum metus vestibulum. Vestibulum in orci quis felis tempor lacinia. Vivamus ornare ultrices facilisis. Ut hendrerit volutpat vulputate. Morbi condimentum venenatis augue, id porta ipsum vulputate in. Curabitur luctus tempus justo. Vestibulum risus lectus, adipiscing nec condimentum quis, condimentum nec nisl. Aliquam dictum sagittis velit sed iaculis. Morbi tristique augue sit amet nulla pulvinar id facilisis ligula mollis. Nam elit libero, tincidunt ut aliquam at, molestie in quam. Aenean rhoncus vehicula hendrerit.

\section{Analysis Of Parity In Fibonacci}

Sed ullamcorper quam eu nisl interdum at interdum enim egestas. Aliquam placerat justo sed lectus lobortis ut porta nisl porttitor. Vestibulum mi dolor, lacinia molestie gravida at, tempus vitae ligula. Donec eget quam sapien, in viverra eros. Donec pellentesque justo a massa fringilla non vestibulum metus vestibulum. Vestibulum in orci quis felis tempor lacinia. Vivamus ornare ultrices facilisis. Ut hendrerit volutpat vulputate. Morbi condimentum venenatis augue, id porta ipsum vulputate in. Curabitur luctus tempus justo. Vestibulum risus lectus, adipiscing nec condimentum quis, condimentum nec nisl. Aliquam dictum sagittis velit sed iaculis. Morbi tristique augue sit amet nulla pulvinar id facilisis ligula mollis. Nam elit libero, tincidunt ut aliquam at, molestie in quam. Aenean rhoncus vehicula hendrerit.

\section{Redrawing the Fibonacci Sequence}

Sed ullamcorper quam eu nisl interdum at interdum enim egestas. Aliquam placerat justo sed lectus lobortis ut porta nisl porttitor. Vestibulum mi dolor, lacinia molestie gravida at, tempus vitae ligula. Donec eget quam sapien, in viverra eros. Donec pellentesque justo a massa fringilla non vestibulum metus vestibulum. Vestibulum in orci quis felis tempor lacinia. Vivamus ornare ultrices facilisis. Ut hendrerit volutpat vulputate. Morbi condimentum venenatis augue, id porta ipsum vulputate in. Curabitur luctus tempus justo. Vestibulum risus lectus, adipiscing nec condimentum quis, condimentum nec nisl. Aliquam dictum sagittis velit sed iaculis. Morbi tristique augue sit amet nulla pulvinar id facilisis ligula mollis. Nam elit libero, tincidunt ut aliquam at, molestie in quam. Aenean rhoncus vehicula hendrerit.

\section{The Fibonacci Decider}

Sed ullamcorper quam eu nisl interdum at interdum enim egestas. Aliquam placerat justo sed lectus lobortis ut porta nisl porttitor. Vestibulum mi dolor, lacinia molestie gravida at, tempus vitae ligula. Donec eget quam sapien, in viverra eros. Donec pellentesque justo a massa fringilla non vestibulum metus vestibulum. Vestibulum in orci quis felis tempor lacinia. Vivamus ornare ultrices facilisis. Ut hendrerit volutpat vulputate. Morbi condimentum venenatis augue, id porta ipsum vulputate in. Curabitur luctus tempus justo. Vestibulum risus lectus, adipiscing nec condimentum quis, condimentum nec nisl. Aliquam dictum sagittis velit sed iaculis. Morbi tristique augue sit amet nulla pulvinar id facilisis ligula mollis. Nam elit libero, tincidunt ut aliquam at, molestie in quam. Aenean rhoncus vehicula hendrerit.

\section{The Fibonacci Picking Function}

Sed ullamcorper quam eu nisl interdum at interdum enim egestas. Aliquam placerat justo sed lectus lobortis ut porta nisl porttitor. Vestibulum mi dolor, lacinia molestie gravida at, tempus vitae ligula. Donec eget quam sapien, in viverra eros. Donec pellentesque justo a massa fringilla non vestibulum metus vestibulum. Vestibulum in orci quis felis tempor lacinia. Vivamus ornare ultrices facilisis. Ut hendrerit volutpat vulputate. Morbi condimentum venenatis augue, id porta ipsum vulputate in. Curabitur luctus tempus justo. Vestibulum risus lectus, adipiscing nec condimentum quis, condimentum nec nisl. Aliquam dictum sagittis velit sed iaculis. Morbi tristique augue sit amet nulla pulvinar id facilisis ligula mollis. Nam elit libero, tincidunt ut aliquam at, molestie in quam. Aenean rhoncus vehicula hendrerit.
